---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# pmird 
<!-- [ -->
```{r pmird_icon, echo = FALSE, eval = FALSE}
knitr::include_graphics("./man/figures/pmird_icon.svg")
```
<!--]{style="float:right"} -->
**R interface to the peatland mid infrared database**

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

<!-- [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)  --> 

pmird is an interface to the peatland mid infrared spectra database (pmird database). 'pmird' allows to access the pmird database as [`dm`](https://dm.cynkra.com/reference/dm.html) object.

The pmird database is a community project, where everybody can contribute and access data. Learn more about [how you can use the data](https://henningte.github.io/pmird/articles/a05-How-to-access-data.html)!

<!-- ### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, pmird, from GitHub with:


```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```
-->

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](https://github.com/henningte/pmird/blob/master/DESCRIPTION) file

**Data :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

### Contributions

We welcome contributions from everyone. Please note that the pmird project is released with a [Contributor Code of Conduct](https://henningte.github.io/pmird//CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
