---
output: github_document
bibliography: "inst/REFERENCES.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# pmird 
<!-- [ -->
```{r pmird_icon, echo = FALSE, eval = FALSE}
knitr::include_graphics("./man/figures/pmird_icon.svg")
```
<!--]{style="float:right"} -->
**R interface to the peatland mid infrared database**

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

<!-- [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)  --> 

pmird is an interface to the peatland mid infrared spectra database (pmird database) [@Teickner.2025c]. 'pmird' allows to access the pmird database as [`dm`](https://dm.cynkra.com/reference/dm.html) object.

The pmird package can be installed as follows:

```{r, eval=FALSE}
remotes::install_github("henningte/pmird")
```

The pmird database can be downloaded from Zotero [@Teickner.2025c]. The downloaded database needs to be imported in a running MariaDB instance. In a linux terminal, the downloaded sql file can be imported like so:

```{bash, eval=FALSE}
mysql -u<user> -p<password> pmird < pmird-backup-2025-04-03.sql
```


Here, <user> and <password> are the respective database user name and password.

The database itself does not contain the infrared spectra. These data are in folder `pmird_prepared_data` which needs to be stored at any place in the file system. 

Once the database is set up and runs in a 'MariaDB' instance, it can be accessed from within R, using the 'RMariaDB' package [@Muller.2021a]:

```{r out-pmird-r-package-connect-db, eval=TRUE, echo=TRUE}
library(pmird)
library(RMariaDB)
library(magrittr)
library(ir)
library(quantities)

# connect to database
con <-
  RMariaDB::dbConnect(
    drv = RMariaDB::MariaDB(),
    dbname = "pmird",
    default.file = "~/my.cnf",
    groups = "rs-dbi"
  )
```

Here, `my.cnf` is a text file that stores user and password information for the database server.

From this on, the 'pmird' R package can be used to access the database. The 'pmird' R package makes use of the R package 'dm' [@Schieferdecker.2022] to access and manipulate the database contents. `pmird::pm_get_dm()` creates a `dm` object which stores the database structure.

```{r out-pmird-r-package-pm-get-dm, eval=TRUE, echo=TRUE}
# create the dm object
dm_pmird <- pmird::pm_get_dm(con, learn_keys = TRUE)
```

The option `learn_keys = TRUE` means that information on the primary and foreign key are added to the dm object.  
A `dm` object is a representation of the entire database and allows comfortable manipulation of the database from within R (e.g. addition of new rows to tables, addition of new tables, data queries) [@Schieferdecker.2022].

## Use case: obtaining general information on the datasets contained in the 'pmird' database {-} 

General information on the datasets contained in the 'pmird' database are stored in table `datasets`. The 'pmird' R package provides a function to obtain this table from the `dm` object (`pmird::pm_get_table(.table_name = "datasets)`).

```{r out-pmird-r-package-pm-get-table-datasets-1, eval=TRUE, echo=TRUE}
# extract the datasets table
pmird_datasets <-
  dm_pmird %>%
  pmird::pm_get_table(.table_name = "datasets")
```

This table can, for example, be used to select studies for which to extract data from the 'pmird' database.


## Use case: extracting data for a specific dataset from the 'pmird' database {-} 

Assume you are interested in viewing all measured data for one specific dataset, e.g. the dataset with `id_dataset == 8` in `pmird_datasets`. Using the 'dm' package and the `dm` object representing the 'pmird' database (`dm_pmird`), this data can be obtained as follows:

```{r out-pmird-r-package-extract-data-1, eval=TRUE, echo=TRUE}
# get data for the dataset with ID 8
d8 <-
  dm_pmird %>%
  dm::dm_zoom_to(datasets) %>%
  dm::filter(id_dataset == 8) %>%
  dm::left_join(samples, by = "id_dataset") %>%
  dm::left_join(data_to_samples, by = "id_sample") %>%
  dm::left_join(data, by = "id_measurement") %>%
  dm::left_join(mir_metadata, by = "id_measurement") %>%
  dm::left_join(macrofossils, by = "id_measurement") %>%
  dm::pull_tbl() %>%
  tibble::as_tibble()
```

The resulting data frame (`d8`) contains information on all samples and measurements for the dataset with `id_dataset == 8`. `d8` does not yet contain any spectra, but stores only information on the respective file paths to the downloaded spectra files within the downloaded folder `pmird_prepared_data`.  
  
To load the spectra, you can use the function `pmird::pmird_load_spectra()`. In addition, you have to specify via argument `directory` in which folder `pmird_prepared_data` is stored (on the computer used for this tutorial, this was `".."`):   

```{r out-pmird-r-package-pm-load-spectra, eval=TRUE, echo=TRUE, warning=FALSE}
# load the spectra
d8 <- pmird::pm_load_spectra(d8, directory = "..")
```

`pm_load_spectra()` is a wrapper function around functions from the package 'ir' [@Teickner.2022e] which in turn are wrappers around `read.spc()` [@Beleites.2021] and `read.csv()`. `pm_load_spectra()` therefore can load spectra both saved as spc and csv files. `pm_load_spectra()` also converts `d8` into an object of class `ir` from the 'ir' package. 'ir' provides functions for spectral preprocessing and manipulation [@Teickner.2022e] and is compatible with the 'irpeat' package which provides functions to analyze peat MIRS and spectral prediction models to predict peat properties from MIRS [@Teickner.2022d].

## Use case: Handling units and measurement errors {-}

The R package 'qauntities' [@Pebesma.2016; @Ucar.2018] can be used to add units and measurement errors to measured variables from the 'pmird' database. The 'pmird' R package allows batch unit and measurement error assignment:

```{r out-pmird-r-package-workflow-quantities-1, eval=TRUE, echo=TRUE}
# add information on units and errors with the 'quantities' package
d8 <-
  d8 %>%
  pmird::pm_add_quantities()

# show some values
head(d8$N, 3)
```


## Use case: Generating data citations {-}

Whoever uses data from the 'pmird' database must cite, in addition to the database, the original data sources for the used datasets. To make this straightforward, the 'pmird' R package contains the function `pm_get_citations()` to generate such a citation list for any extracted data subset:

```{r, out-pmird-r-package-workflow-citations-1, eval=TRUE, echo=TRUE}
# collect all citations for `d8`:
d8_citations <- 
  pm_get_citations(
    con = con,
    x = d8$id_measurement, 
    file = "d8_citations.bib"
  )

# close connection to database
RMariaDB::dbDisconnect(con)
```

```{r, include=FALSE}
file.remove("d8_citations.bib")
```

The function takes column `id_measurement` of the extracted data and collects citations for all relevant data sources from the database. The results are exported to a bibtex file which is defined via argument `file`. This file can be imported to literature reference software. In this case, since the data have not been previously published, the created bibtex file is empty. `RMariaDB::dbDisconnect(con)` closes the connection to the database, as this is the final use case presented here. 


<!-- ### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, pmird, from GitHub with:


```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```
-->

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](https://github.com/henningte/pmird/blob/master/DESCRIPTION) file

**Data :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

### Contributions

We welcome contributions from everyone. Please note that the pmird project is released with a [Contributor Code of Conduct](https://henningte.github.io/pmird//CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


### References
