---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# pmird
**peat mid infrared spectra data compendium**


<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

<!-- [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)  --> 

pmird is an R package that has the aim to provide a comprehensive and easily to access data collection of mid infrared spectra (MIR) of peat and related material (for example peat forming vegetation or DOM).

pmird is designed as community-based project, meaning that everybody can contribute and benefit from this project. Learn more about [why you should contribute](https://henningte.github.io/pmird/articles/a01-Why-to-contribute.html) to pmird and [how you can use the data](https://henningte.github.io/pmird/articles/a05-How-to-access-data.html)!

pmird is part of my PhD project. I want to be fully transparent on [what I plan to do with the data](https://henningte.github.io/pmird/articles/a02-What-I-plan-to-do-with-the-data.html).

<!-- ### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, pmird, from GitHub with:


```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```
-->

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

