---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# pmird 
<!-- [ -->
```{r pmird_icon, echo = FALSE, eval = FALSE}
knitr::include_graphics("./man/figures/pmird_icon.svg")
```
<!--]{style="float:right"} -->
**peat mid infrared spectra data compendium**

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

<!-- [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)  --> 

pmird is an R package that has two major aims: 

1. Provide a comprehensive and easily to access data collection of mid infrared spectra (MIR) of peat and related material (for example peat forming vegetation or dissolved organic matter).

2. Combine this with additional data on peat characteristics, such as bulk density or carbon content, to support the development of MIR prediction models for these characteristics.

pmird is a community-based project, where everybody can contribute and access data. Learn more about [how you can use the data](https://henningte.github.io/pmird/articles/a05-How-to-access-data.html)!

<!-- ### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, pmird, from GitHub with:


```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```
-->

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](https://github.com/henningte/pmird/blob/master/DESCRIPTION) file

**Data :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

### Contributions

We welcome contributions from everyone. Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

If you want to contribute to the code, please see our [code contributor guidelines](CONTRIBUTING.md).
