---
title: "pmird_prepare_data_DATA_ID"
author: "Henning Teickner"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

```{r packages}
library(pmird)
```

```{r}
# directory
dir_source <- "../pmird_raw_data/FOLDER_WITH_DATA"
dir_target <- "../pmird_prepared_data/FOLDER_WITH_DATA"
# dir.create(dir_target, recursive = FALSE)
# dir.create(paste0(dir_target, "/mir"), recursive = FALSE)
```

# Introduction

Script to prepare the data in `c00001-2020-08-17-Hodgkins` for pmird.

# Load required files

```{r connect-db}
# connect to database
con <-
  RMariaDB::dbConnect(
    drv = RMariaDB::MariaDB(),
    dbname = "pmird",
    username = "root", # ---todo: adjust or get from config file
    password = "coucou",
    host = "mariadb"
  )

# pmird database
dm_pmird <-
  pmird::pm_get_dm(con, learn_keys = TRUE)
```

```{r identifiers}
# general information (ids)
id_dataset <-
  dm_pmird %>%
  dm::dm_zoom_to(datasets) %>%
  pmird::pm_get_max(.col = id_dataset) %>%
  magrittr::add(1L)

id_measurement_last <-
  dm_pmird %>%
  dm::dm_zoom_to(data) %>%
  pmird::pm_get_max(.col = id_measurement)

id_sample_last <-
  dm_pmird %>%
  dm::dm_zoom_to(samples) %>%
  pmird::pm_get_max(.col = id_sample)

id_coverage_last <-
  dm_pmird %>%
  dm::dm_zoom_to(coverages) %>%
  pmird::pm_get_max(.col = id_coverage)

id_geographic_coverage_last <-
  dm_pmird %>%
  dm::dm_zoom_to(geographic_coverages) %>%
  pmird::pm_get_max(.col = id_geographic_coverage)

id_temporal_coverage_last <-
  dm_pmird %>%
  dm::dm_zoom_to(temporal_coverages) %>%
  pmird::pm_get_max(.col = id_temporal_coverage)

id_taxonomic_coverage_last <-
  dm_pmird %>%
  dm::dm_zoom_to(taxonomic_coverages) %>%
  pmird::pm_get_max(.col = id_taxonomic_coverage)

id_change_history_last <-
  dm_pmird %>%
  dm::dm_zoom_to(change_histories) %>%
  pmird::pm_get_max(.col = id_change_history)

id_instrument_last <-
  dm_pmird %>%
  dm::dm_zoom_to(instruments) %>%
  pmird::pm_get_max(.col = id_instrument)

id_method_last <-
  dm_pmird %>%
  dm::dm_zoom_to(methods) %>%
  pmird::pm_get_max(.col = id_method)

id_method_step_last <-
  dm_pmird %>%
  dm::dm_zoom_to(method_steps) %>%
  pmird::pm_get_max(.col = id_method_step)

id_quality_control_last <-
  dm_pmird %>%
  dm::dm_zoom_to(quality_control) %>%
  pmird::pm_get_max(.col = id_quality_control)

id_person_last <-
  dm_pmird %>%
  dm::dm_zoom_to(persons) %>%
  pmird::pm_get_max(.col = id_person)

id_taxonomic_classification_last <-
  dm_pmird %>%
  dm::dm_zoom_to(taxonomic_classifications) %>%
  pmird::pm_get_max(.col = id_taxonomic_classification)

id_macrofossil_type_last <-
  dm_pmird %>%
  dm::dm_zoom_to(macrofossil_types) %>%
  pmird::pm_get_max(.col = id_macrofossil_type)
```


# Add data to template files

## pmird.data

Describe reformatting

```{r data-preparation}
### extract individual mid infrared spectra

### code to format data
```

### pmird.samples

```{r samples}
# combine
samples <- 
  pmird:::db_template_tables$samples %>%
  dplyr::bind_rows() %>%
  dplyr::select(dplyr::one_of(pmird:::db_template_tables$samples %>% colnames())) %>%
  dplyr::mutate(id_dataset = !!id_dataset,
                id_sample = id_sample_last + seq_len(nrow(.)))
```

### pmird.data

```{r data}
# combine
d <- 
  pmird:::db_template_tables$data %>%
  dplyr::bind_rows() %>%
  dplyr::select(dplyr::one_of(pmird:::db_template_tables$data %>% colnames())) %>%
  dplyr::mutate(id_measurement = id_measurement_last + seq_len(nrow(.)))
```

### pmird.data_to_samples

```{r data_to_samples}
data_to_samples <-  
  pmird:::db_template_tables$data_to_samples %>%
  dplyr::bind_rows(
  )
```


## pmird.mir_metadata

```{r mir_metadata}
mir_metadata <-
  pmird::db_template_tables$mir_metadata %>%
  dplyr::bind_rows(
  )
```


## pmird.change_histories

Add entries here if you change the data (not necessary upon initialization)

```{r change_histories}
change_histories <- 
  pmird:::db_template_tables$change_histories %>%
  dplyr::bind_rows()
```

## pmird.citations

_Note_: use the script `add-citations.Rmd` to add new literature references to the database. 

This chunk here is only to query those references required for this dataset to get e.g. author names, or publication dates, and to link citations to other information (e.g. methods). 

```{r citations}
# bibliography information
tmp_file <- tempfile("temp_bib", tmpdir = tempdir(), fileext = ".bib")

dm_pmird %>%
  dm::dm_zoom_to(citations) %>%
  dplyr::filter(id_citation %in% c()) %>% # put bibtex keys here
  dplyr::pull(bibtex) %>%
  writeLines(con = tmp_file)

citations <- bib2df::bib2df(tmp_file)

# Note: The article serving as reference for the data should be replaced later on by the published article, unless this article does not comprise all available data
bibliography_information <- 
  bib2df::bib2df(tmp_file) %>%
  dplyr::filter(BIBTEXKEY == "") # put bibtex keys here
```

## pmird.citations_to_data

_Note_: There are no sample-specific citations for this dataset.

```{r citations_to_data}
citations_to_data <-
  pmird:::db_template_tables$citations_to_data %>%
  dplyr::bind_rows( 
    # e.g. csv table with sample labels/ids and bibtex keys
  )
```

## pmird.coverages

### pmird.geographic_coverages

```{r geographic_coverages}
# get bounding box of data
d_bbx <-
  d %>%
  dplyr::filter(!is.na(sampling_latitude)) %>%
  sf::st_as_sf(coords = c("sampling_longitude", "sampling_latitude"), 
               crs = "EPSG:3857") %>%
  sf::st_bbox()

# description
geographic_description_file <- paste0(dir_source, "/additional/geographic_description.md")

geographic_coverages <-
  pmird:::db_template_tables$geographic_coverages %>%
  dplyr::bind_rows(
    tibble::tibble( # bounding box for complete dataset
      id_geographic_coverage = id_geographic_coverage_last + 1L,
      id_coverage = id_coverage_last + 1L,
      geographic_description = 
        readChar(geographic_description_file, file.info(geographic_description_file)$size),
      west_bounding_coordinate = d_bbx[["xmin"]],  
      east_bounding_coordinate = d_bbx[["xmax"]],  
      north_bounding_coordinate = d_bbx[["ymax"]], 
      south_bounding_coordinate = d_bbx[["ymin"]]
    )
  )
```

### pmird.temporal_coverages

_Note:_ No sampling date is given in the data or thesis. Only the sampling year is known.

```{r temporal_coverages}
temporal_coverages <-
  pmird:::db_template_tables$temporal_coverages %>%
  dplyr::bind_rows(
    tibble::tibble( # bounding box for complete dataset
      id_temporal_coverage = id_temporal_coverage_last + 1L,
      id_coverage = max(geographic_coverages$id_coverage) + 1L,
      begin_date = min(d$sampling_date, na.rm = TRUE),
      end_date = max(d$sampling_date, na.rm = TRUE)
    )
  )
```

### pmird.taxonomic_classifications

```{r taxonomic_classifications}
taxonomic_classifications <-
  pmird::db_template_tables$taxonomic_classifications %>%
  dplyr::bind_rows(
  ) %>%
  pmird:::pm_update_import(
    con = con, 
    table_name = "taxonomic_classifications", 
    id_last = id_taxonomic_classification_last
  )

taxonomic_classifications_required <-
  taxonomic_classifications$required

taxonomic_classifications <-
  taxonomic_classifications$to_add
```


### pmird.taxonomic_coverages

```{r taxonomic_coverages}
# get unique taxonomic_coverages
taxonomic_coverages <-
  pmird:::db_template_tables$taxonomic_coverages %>%
  dplyr::bind_rows(
    tibble::tibble(
      id_taxonomic_coverage = id_taxonomic_coverage_last + 1L,
      id_coverage = max(temporal_coverages$id_coverage) + length(id_taxonomic_coverage)
    )
)
```


### pmird.taxclas_to_taxcovs

```{r taxclas_to_taxcovs}
taxclas_to_taxcovs <- pmird::db_template_tables$taxclas_to_taxcovs %>%
  dplyr::bind_rows(
    tibble::tibble(
      id_taxonomic_coverage = 
        taxonomic_coverages %>% 
        dplyr::pull(id_taxonomic_coverage),
      id_taxonomic_classification = 
        taxonomic_classifications_required %>% 
        dplyr::pull(id_taxonomic_classification)
    )
  )
```


### pmird.coverages

```{r coverages}
# collect coverages
coverages <-
  pmird:::db_template_tables$coverages %>%
  dplyr::bind_rows(
    geographic_coverages %>%
      dplyr::select(id_coverage) %>%
      dplyr::mutate(coverage_type = "geographic_coverage"),
    temporal_coverages %>%
      dplyr::select(id_coverage) %>%
      dplyr::mutate(coverage_type = "temporal_coverage"),
    taxonomic_coverages %>%
      dplyr::select(id_coverage) %>%
      dplyr::mutate(coverage_type = "taxonomic_coverage")
  )
```


## pmird.macrofossil_types

```{r macrofossil_types}
macrofossil_types <-
  pmird::db_template_tables$macrofossil_types %>%
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/additional/macrofossil_types.csv")) %>%
      dplyr::left_join(taxonomic_classifications_required %>%
                         dplyr::select(-common_name), 
                       by = c("taxon_rank_name", "taxon_rank_value"))  %>% 
      dplyr::select(-number_type)
  ) %>%
  pmird:::pm_update_import(
    con = con, 
    table_name = "macrofossil_types", 
    id_last = id_macrofossil_type_last
  ) %>%
  purrr::map(dplyr::select, -taxon_rank_name, -taxon_rank_value)

macrofossil_types_required <-
  macrofossil_types$required

macrofossil_types <-
  macrofossil_types$to_add
```

## pmird.mactyps_to_taxclas

```{r mactyps_to_taxclas}
mactyps_to_taxclas <-
  pmird::db_template_tables$mactyps_to_taxclas %>%
  dplyr::bind_rows(
    macrofossil_types %>%
      dplyr::filter(!is.na(id_taxonomic_classification)) %>%
      dplyr::select(id_macrofossil_type, id_taxonomic_classification)
  )

# update macrofossil_types_required and macrofossil_types_required
macrofossil_types_required <-
  macrofossil_types_required %>%
  dplyr::select(-id_taxonomic_classification)

macrofossil_types <-
  macrofossil_types %>%
  dplyr::select(-id_taxonomic_classification)
```


## pmird.macrofossils

```{r macrofossils}
# prepare data

# add id_sample
d2 <-
  d2 %>%
  dplyr::rename(sample_label = "sample_id") %>%
  dplyr::left_join(d %>% dplyr::select(id_sample, sample_label),
                   by = c("sample_label")) %>%
  dplyr::select(-sample_label)

# collate two columns with identical macrofossil_type
d2 <-
  d2 %>%
  dplyr::mutate(
    `Tetronicum.magellanicum...epiderms..rootlets....` =
      dplyr::case_when(
        is.na(`Tetronicum.magellanicum...epiderms..rootlets....`) ~ `cf..Tetronicum.magellanicum...epiderms..rootlets....`,
        TRUE ~ `Tetronicum.magellanicum...epiderms..rootlets....`
      )
  ) %>%
  dplyr::select(-`cf..Tetronicum.magellanicum...epiderms..rootlets....`)

# reformat
index <-
  read.csv(paste0(dir_source, "/additional/macrofossil_types.csv")) %>%
  dplyr::pull(number_type)

d2_id_sample <-
  d2 %>%
  dplyr::pull(id_sample)

d2 <- 
  d2 %>%
  dplyr::select(-id_sample)

d2 <-
  purrr::map_df(seq_len(ncol(d2)), function(i) {
    tibble::tibble(
      id_sample = d2_id_sample,
      id_macrofossil_type = macrofossil_types_required$id_macrofossil_type[[i]],
      macrofossil_volume_fraction = 
        if(index[[i]] == "fraction") d2[, i, drop = TRUE] else NA_real_,
      macrofossil_count = 
        if(index[[i]] == "count") d2[, i, drop = TRUE] else NA_real_,
      macrofossil_presence = 
        if(index[[i]] == "logical") d2[, i, drop = TRUE] else NA_real_
    )  
  }) %>%
  dplyr::mutate(
    macrofossil_presence = dplyr::case_when(
      macrofossil_volume_fraction > 0 | macrofossil_count > 0 | macrofossil_presence == 1 ~ 1L,
      TRUE ~ 0L
    )
  ) %>%
  dplyr::filter(!is.na(macrofossil_presence))

macrofossils <-
  pmird::db_template_tables$macrofossils %>%
  dplyr::bind_rows(
    d2
  )
```


## pmird.custom_units

_Note_: Add new units in the script `001-db_initialize.Rmd`.


## pmird.instruments

```{r instruments}
instruments <-
  pmird:::db_template_tables$instruments %>%
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/additional/instruments.csv"), as.is = TRUE)
  ) %>%
  pmird::pm_update_import(
    con = con, 
    table_name = "instruments", 
    id_last = id_instrument_last
  )
  
instruments_required <-
  instruments$required

instruments <-
  instruments$to_add
```


## pmird.quality_control

### pmird.quality_control

```{r quality_control}
quality_control <-
  pmird::db_template_tables$quality_control %>%
  dplyr::bind_rows(
  )
```

### pmird.citations_to_quality_control

_Note_: For this dataset, no literature was cited for the quality control

```{r citations_to_quality_control}
citations_to_quality_control <-
  pmird::db_template_tables$citations_to_quality_control %>%
  dplyr::bind_rows()
```

## pmird.methods

### pmird.method_steps

```{r method_steps}
method_steps <-
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/additional/method_steps.csv")) %>%
      dplyr::mutate(
        description = 
          purrr::map_chr(description, function(x) {
            if(stringr::str_detect(x, pattern = "\\.md$")) {
              x <- paste0(dir_source, "/additional/", x)
              readChar(x, file.info(x)$size)
            } else {
              x
            }
          })
      )
  ) %>%
  pmird:::pm_update_import(
    con = con, 
    table_name = "method_steps", 
    id_last = id_method_step_last
  )

method_steps_required <-
  method_steps$required

method_steps <-
  method_steps$to_add
```

### pmird.citations_to_method_steps

```{r citations_to_method_steps}
citations_to_method_steps <- 
  pmird::db_template_tables$citations_to_method_steps %>%
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/additional/citations_to_method_steps.csv"))
  )

id_method_step <-
  method_steps_required %>%
  dplyr::slice(!!citations_to_method_steps$id_method_step) %>%
  dplyr::pull(id_method_step)

citations_to_method_steps <-
  citations_to_method_steps %>%
  dplyr::mutate(id_method_step = !!id_method_step)
```

### pmird.method_steps_to_instruments

```{r method_steps_to_instruments}
method_steps_to_instruments <-  
  pmird::db_template_tables$method_steps_to_instruments %>%
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/additional/method_steps_to_instruments.csv"))
  )

id_method_step <-
  method_steps_required %>%
  dplyr::slice(!!method_steps_to_instruments$id_method_step) %>%
  dplyr::pull(id_method_step)

id_instrument <-
  instruments_required %>%
  dplyr::slice(!!method_steps_to_instruments$id_instrument) %>%
  dplyr::pull(id_instrument)

method_steps_to_instruments <-
  method_steps_to_instruments %>%
  dplyr::mutate(
    id_method_step = !!id_method_step,
    id_instrument = !!id_instrument)
```

### pmird.quality_control_to_method_steps

_Note_: For this dataset, all quality controls are described on the methods level.

```{r quality_control_to_method_steps}
quality_control_to_method_steps <-
  pmird::db_template_tables$quality_control_to_method_steps %>%
  dplyr::bind_rows(
  )
```


### pmird.methods_to_method_steps

_Note_: This data frame is further modified in the methods chunk.

```{r method_steps_to_methods}
methods_to_method_steps <-
  pmird::db_template_tables$methods_to_method_steps %>%
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/additional/methods_to_method_steps.csv")) 
  )

id_method_step <-
  method_steps_required %>%
  dplyr::slice(!!methods_to_method_steps$id_method_step) %>%
  dplyr::pull(id_method_step)

methods_to_method_steps <-
  methods_to_method_steps %>%
  dplyr::mutate(
    id_method_step = !!id_method_step
  )
```


### pmird.methods

```{r methods}
methods <-
  pmird::db_template_tables$methods %>%
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/additional/methods.csv")) %>%
      dplyr::mutate(
        sampling_description = 
          purrr::map_chr(sampling_description, function(x) {
            if(is.na(x)) {
              x
            } else if(stringr::str_detect(x, pattern = "\\.md$")) {
              x <- paste0(dir_source, "/additional/", x)
              readChar(x, file.info(x)$size)
            }
          })
      ) %>%
      dplyr::left_join(methods_to_method_steps, by = "id_method")
  ) %>%
  pmird:::pm_update_import(
    con = con, 
    table_name = "methods", 
    id_last = id_method_last
  ) %>%
  purrr::map(dplyr::select, -comments, -id_method_step)

methods_required <-
  methods$required

methods <-
  methods$to_add

# update id in methods_to_method_steps
id_method <-
  methods_required %>%
  dplyr::slice(!!methods_to_method_steps$id_method) %>%
  dplyr::pull(id_method)

methods_to_method_steps <-
  methods_to_method_steps %>%
  dplyr::mutate(
    id_method = !!id_method
  )
```


### pmird.citations_to_methods

```{r citations_to_methods}
citations_to_methods <-
  methods_required %>%
  dplyr::left_join(methods_to_method_steps, by = "id_method") %>%
  dplyr::left_join(citations_to_method_steps, by = "id_method_step") %>%
  dplyr::select(id_method, id_citation) %>%
  dplyr::distinct()

# check
# dplyr::left_join(methods_to_method_steps, methods, by = c("id_method")) %>% dplyr::left_join(method_steps, by = "id_method_step") %>%  dplyr::left_join(citations_to_methods, by = "id_method") %>% View()
```

## pmird.datasets

### pmird.datasets

Add information on datasets

```{r datasets}
intellectual_rights_file <- paste0(dir_source, "/additional/permission.md")
acknowledgements_file <- paste0(dir_source, "/additional/acknowledgements.md")
abstract_file <- paste0(dir_source, "/additional/abstract.md")
refrence_publication <-
  dm_pmird %>%
  dm::dm_zoom_to(citations) %>%
  dplyr::filter(id_citation %in% c("Munchberger.2019", "Munchberger.2019a")) %>%
  dplyr::pull(bibtex) %>%
  paste(collapse = "\n\n")

datasets <-
  db_template_tables$datasets %>%
  dplyr::bind_rows(
    tibble::tibble(
      id_dataset = id_dataset,
      title = "Peat core data from two peatlands in Tierra del Fuego",
      pub_date = citations$YEAR[citations$BIBTEXKEY == "Munchberger.2019"],
      language = citations$LANGID[citations$BIBTEXKEY == "Munchberger.2019"],
      abstract = 
        readChar(abstract_file, file.info(abstract_file)$size),
      intellectual_rights = 
        readChar(intellectual_rights_file, file.info(intellectual_rights_file)$size),
      id_license = 
        dm_pmird %>%
        dm::dm_zoom_to(licenses) %>%
        dplyr::filter(identifier == "CC BY 4.0") %>% 
        dplyr::pull(id_license),
      id_maintenance = 1L,
      id_method = methods$id_method[[1]],
      purpose = NA_character_,
      introduction = NA_character_,
      getting_started = NA_character_, # ---todo
      acknowledgements = 
        readChar(acknowledgements_file, file.info(acknowledgements_file)$size),
      reference_publication = refrence_publication
    )
  )
```

### pmird.citations_to_datasets

```{r citations_to_datasets}
citations_to_datasets <-
  pmird::db_template_tables$citations_to_datasets %>%
  dplyr::bind_rows(
    tibble::tibble(
      id_dataset = datasets$id_dataset,
      id_citation = citations$BIBTEXKEY
    )
  )
```

### pmird.attributes_to_datasets_to_methods

```{r attributes_to_datasets_to_methods}
# write attribute_names to a csv file #---note: don't overwrite here
if(!file.exists(paste0(dir_source, "/additional/attributes_to_datasets_to_methods.csv"))) {
  RMariaDB::dbGetQuery(con, "SELECT * FROM `attributes`") %>%
    dplyr::select(attribute_name) %>%
    dplyr::mutate(id_method = NA_integer_) %>%
    write.csv(paste0(dir_source, "/additional/attributes_to_datasets_to_methods.csv"), 
            row.names = FALSE)
}

# make sure that attribute ids match even if later additional attributes are added anywhere
attributes_to_datasets_to_methods <-
  pmird::db_template_tables$attributes_to_datasets_to_methods %>%
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/additional/attributes_to_datasets_to_methods.csv")) %>%
      dplyr::right_join(RMariaDB::dbGetQuery(con, "select * from attributes"), 
                        by = "attribute_name") %>%
      dplyr::arrange(id_attribute) %>%
      dplyr::select(id_attribute, id_method) %>%
      dplyr::mutate(id_dataset = !!datasets$id_dataset) %>% 
      dplyr::filter(!is.na(id_method))
  )

# update id_method
id_method <-
  methods_required %>%
  dplyr::slice(!!attributes_to_datasets_to_methods$id_method) %>%
  dplyr::pull(id_method)

attributes_to_datasets_to_methods <-
  attributes_to_datasets_to_methods %>%
  dplyr::mutate(
    id_method = !!id_method
  )

# check
# dplyr::left_join(attributes_to_datasets_to_methods, dbGetQuery(con, "select * from attributes"), by = "id_attribute") %>% dplyr::left_join(methods_to_method_steps, by = "id_method") %>% dplyr::left_join(method_steps, by = "id_method_step") %>% View()
```

### pmird.datasets_to_coverages

```{r datasets_to_coverages}
datasets_to_coverages <-
  pmird::db_template_tables$datasets_to_coverages %>%
  dplyr::bind_rows(
    tibble::tibble(
      id_dataset = datasets$id_dataset,
      id_coverage = coverages$id_coverage
    )
  )
```


## pmird.licenses

_Note_: Please add licenses with script `add-licenses.Rmd`.


## pmird.maintenances

```{r maintenances}
maintenances <-
  pmird:::db_template_tables$maintenances %>%
  dplyr::bind_rows(
  )
```

## pmird.maintenances_to_change_histories

_Note_: For this dataset, no changes exist yet.

```{r maintenances_to_change_histories}
maintenances_to_change_histories <-
  pmird::db_template_tables$maintenances_to_change_histories %>%
  dplyr::bind_rows()
```



## pmird.persons

```{r persons}
persons <-
  pmird::db_template_tables$persons %>%
  dplyr::bind_rows(
    read.csv(paste0(dir_source, "/authors_WM.csv")) %>%
      dplyr::slice(-1) %>%
      dplyr::rename(
        sur_name = "author_surname",
        given_name = "author_given_name",
        electronic_mail_address = "author_email_address"
      ) %>%
      dplyr::select(sur_name, given_name, electronic_mail_address) %>%
      dplyr::mutate(
        electronic_mail_address = 
          dplyr::case_when(
            !sur_name %in% c("Münchberger", "Knorr") ~ NA_character_,
            TRUE ~ electronic_mail_address
          )
      )
    ) %>%
  dplyr::bind_rows(
    tibble::tibble(
      sur_name = "Gałka",
      given_name = "Mariusz"
    )
  ) %>%
  dplyr::mutate(id_person = seq_len(nrow(.))) %>%
  pmird:::pm_update_import(
    con = con, 
    table_name = "persons", 
    id_last = id_person_last
  )

persons_required <-
  persons$required

persons <-
  persons$to_add
```

## pmird.contacts

-- todo: add and move behind ## pmird.persons

```{r contacts}
contacts <-
  pmird::db_template_tables$contacts %>%
  dplyr::bind_rows(
    tibble::tibble(
      id_dataset = datasets$id_dataset,
      id_person = persons$id_person[[1]] # author of the thesis
    )
  )
```


# Add data to pmird

```{r into-pmird}
dm_insert_in <-
  dm::dm(
    geographic_coverages = geographic_coverages,
    temporal_coverages = temporal_coverages,
    taxonomic_coverages = taxonomic_coverages,
    taxonomic_classifications = taxonomic_classifications,
    taxclas_to_taxcovs = taxclas_to_taxcovs,
    coverages = coverages,
    instruments = instruments,
    method_steps = method_steps,
    quality_control = quality_control,
    methods = methods,
    maintenances = maintenances,
    change_histories = change_histories,
    maintenances_to_change_histories = maintenances_to_change_histories,
    persons = persons,
    datasets = datasets,
    macrofossil_types = macrofossil_types,
    mactyps_to_taxclas = mactyps_to_taxclas,
    samples = samples
    ) %>%
  dm::copy_dm_to(con, ., temporary = TRUE)

dm_insert_out <-
  dm_pmird %>%
  dm::dm_rows_insert(dm_insert_in, in_place = TRUE)

dbAppendTable(con, name = "data", value = d)

dm_pmird <-
  pmird::pm_get_dm(con, learn_keys = TRUE)

dm_insert_in <-
  dm::dm(
    data_to_samples = data_to_samples,
    mir_metadata = mir_metadata,
    macrofossils = macrofossils,
    contacts = contacts,
    citations_to_methods = citations_to_methods,
    citations_to_quality_control = citations_to_quality_control,
    citations_to_method_steps = citations_to_method_steps,
    citations_to_samples = citations_to_samples,
    citations_to_datasets = citations_to_datasets,
    method_steps_to_instruments = method_steps_to_instruments,
    methods_to_method_steps = methods_to_method_steps,
    # methods_to_coverages = methods_to_coverages, # not in this dataset
    quality_control_to_method_steps = quality_control_to_method_steps,
    attributes_to_datasets_to_methods = attributes_to_datasets_to_methods,
    datasets_to_coverages = datasets_to_coverages
    ) %>%
  dm::copy_dm_to(con, ., temporary = TRUE)

dm_insert_out <-
  dm_pmird %>%
  dm::dm_rows_insert(dm_insert_in, in_place = TRUE)
```

```{r disconnect}
RMariaDB::dbDisconnect(con)
```

# Todo
